% Christian Oudard's Resume
% Formatting adapted from: http://www.mcnabbs.org/andrew/linux/latexres/

\documentclass[11pt,oneside]{article}

\hyphenpenalty=300

\usepackage{xltxtra,fontspec,xunicode}
\defaultfontfeatures{Scale=MatchLowercase}
\setmainfont{Volkhov}
\setsansfont{Istok Web}

\usepackage{geometry}

\pagestyle{empty}
\geometry{
    letterpaper,
    tmargin=1in,
    bmargin=1in,
    lmargin=1in,
    rmargin=1in,
    headheight=0in,
    headsep=0in,
    footskip=.3in,
}
\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{5pt}

\newenvironment{ressection}[1]{
    \textrm{\Large#1}
    \begin{itemize}
}{
    \end{itemize}
}

\newcommand{\resitem}[1]{
    \item \begin{flushleft} \textsf{#1} \end{flushleft}
}

\newcommand{\ressubitem}[1]{
    \item \begin{flushleft} \textsf{#1} \end{flushleft}
}

\newcommand{\resbigitem}[3]{
    \item
    \textrm{#1}
    \hspace{5pt}
    \textit{#2}
    \hfill
    \textit{#3}
}

\newenvironment{ressubsec}[3]{
    \resbigitem{#1}{#2}{#3}
    \begin{itemize}
}{
    \end{itemize}
}

\newenvironment{reslist}[1]{
    \resitem{\textsf{#1}}
    \begin{itemize}
}{
    \end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Name
\begin{center}
    \textrm{\Huge Christian Oudard} \\
    \vspace{4pt}
    \textsf{
        christian.oudard@gmail.com \\
        http://github.com/christian-oudard/
    }
\end{center}
\vspace{8pt} 

\textrm{\Large Summary}\par
\vspace{8pt}
\textsf{I solve problems by creating clear understanding, and then turning that understanding
into software. I'm an experienced programmer, specializing in Python and full-stack web
development. My other areas of interest include graphics, machine learning, and finance.
On a personal level, I care deeply about communicating empathetically, in a way that
respects the humanity of others. As far as topics outside of software, let's
talk about math, physics, cognition, or biomechanics.}

\vspace{12pt}


\begin{ressection}{Skills}
    \resitem{
        \textrm{Languages:}
        Python,
        Ruby,
        Haskell,
        Shell Script
        JavaScript,
        SQL,
        HTML,
        CSS,
    }

    \resitem{
        \textrm{Libraries:}
        NumPy,
        TensorFlow,
        Django,
        Ruby on Rails,
        jQuery
    }

    \resitem{
        \textrm{Tools and Platforms:}
        Linux,
        Git,
        Puppet,
        Amazon Web Services (AWS),
        Google Cloud Platform (GCP)
    }
\end{ressection}


\begin{ressection}{Experience}

    \begin{ressubsec}{Independent Software Developer}{}{November 2017\textendash Present}
        \ressubitem{Please ask me in person about clients and projects}
    \end{ressubsec}

    \begin{ressubsec}{Bonsai AI}{Backend Developer}{March 2017\textendash October 2017}
        \ressubitem{Wrote Python code and tests to build the Bonsai reinforcement learning (RL) platform.}
        \ressubitem{DevOps work, including server deployment and maintenance.}
        \ressubitem{Worked with the AI research team to help implement recent RL research from DeepMind and others.}
    \end{ressubsec}

    \begin{ressubsec}{Disqus}{Data Engineer}{June 2016\textendash December 2016}
        \ressubitem{Part of a three-person team responsible for a data analysis pipeline handling tens of millions of events per day. The pipeline is built using Kafka, Storm, S3, Hive, and Redshift.}
        \ressubitem{Backend feature development in Python, including work on advertisement serving.}
    \end{ressubsec}

    \begin{ressubsec}{Infer Inc.}{Full-stack Engineer}{July 2015\textendash September 2015}
        \ressubitem{Worked on Infer's main product which manages machine learning sales models.}
        \ressubitem{Coded improvements to the CoffeeScript frontend interface as well as the Python backend.}
    \end{ressubsec}

    \begin{ressubsec}{TinyCo}{Backend Engineer}{September 2012\textendash January 2014}
        \ressubitem{Coded complete rewrites of several major systems, such as the code deployment system and game configuration server.}
        \ressubitem{Interviewed new employees to help grow the team from 3 to 8.}
        \ressubitem{Mentored junior backend engineers and mobile engineers, especially in Python and Django.}
        \ressubitem{Instituted the usage of better database migration practices, and better unit testing.}
    \end{ressubsec}

    \begin{ressubsec}{Scribd}{Software Engineer}{January 2012\textendash August 2012}
        \ressubitem{Worked as a Ruby on Rails and Javascript engineer on a team of 12.}
        \ressubitem{Worked with a huge mysql database. We ran out of 32-bit unsigned primary keys on one of our tables.}
        \ressubitem{Responsibilities included the Scribd Developer API, internal mobile client API, and the embedded document viewer.}
    \end{ressubsec}

    \begin{ressubsec}{PolicyStat}{Software Engineer}{October 2008\textendash January 2012}
        \ressubitem{Joined at a very early stage, when there was just the CTO, the CEO, and a single client. When I left, we had over a hundred hospitals as customers.}
        \ressubitem{Did full-stack development, including server administration on Amazon AWS, Django backend, and web frontend using jQuery and CSS}
        \ressubitem{With the CTO, completely rewrote the codebase from PHP to Python/Django.}
        \ressubitem{Developed an algorithm for diffing structured documents in HTML.}
    \end{ressubsec}

\end{ressection}


\begin{ressection}{Education}

  \resbigitem{University of Louisville}{Bachelors of Computer Science}{Fall 2004\textendash Spring 2008}

\end{ressection}


\end{document}
